hormones

### 2019-12-31 analysis/07_hormones.Rmd
better figures, with and without stats

```{r setup}
library(tidyverse)
library(cowplot)
library(readxl)
library(modelr)
library(lubridate)

@@

>>>>

```{r setup}
library(tidyverse)
library(cowplot)
library(readxl)
library(modelr)
library(lubridate)
library(ggsignif)

@@

## for rechelle

```{r forrechelle, fig.height= 4, fig.width=6}

rechelle <- hormones %>%
  dplyr::filter(hormone %in% c("prolactin", "cort"),
                treatment %in% c("lay", "inc.d9", "hatch", "n9")) %>%
  dplyr::select(-icons, -music, -iconpath, -okay)

rechelle$hormone <- factor(rechelle$hormone, levels = c("prolactin", "cort"))

prl.rechelle <- rechelle %>% filter(hormone == "prolactin")   %>%  droplevels()
cort.rechelle <- rechelle %>% filter(hormone == "cort")   %>%  droplevels()

TukeyHSD(aov(plasma_conc ~  treatment, data=prl.rechelle))
TukeyHSD(aov(plasma_conc ~  treatment, data=cort.rechelle))

rechelleplot <- function(mydf, myylab){

  p <- ggplot(mydf, aes(x = treatment, y = plasma_conc, fill = sex)) +
  geom_point(aes(color = sex), position = position_dodge(0.9), size = 2)+
  geom_boxplot(alpha = 0.5, outlier.shape = NA) +
  scale_color_manual(name = "Sex", values = c("gray50", "maroon"))+
  scale_fill_manual(name = "Sex", values = c("gray50", "maroon"))+

  theme(axis.text.x = element_text(angle = 45, hjust = 1),
         legend.position = "none",
          strip.text = element_blank()) +
    theme_classic()+
  theme(text = element_text(size= 15)) +
    labs(x = "Stage", y = myylab) 
  return(p)

}

#PRL
rechelleplot(prl.rechelle, "Prolactin (ng/mL)")
rechelleplot(prl.rechelle, "Prolactin (ng/mL)") + 
  scale_y_continuous(breaks = c(0,25,50,75,100, 125), limits = c(-20,125)) +
  geom_signif(comparisons=list(c("lay", "hatch")), annotations= "p < 0.001", y_position = 100, tip_length = 0.05, vjust = 0, color= "black" , textsize = 5 ) +
  geom_signif(comparisons=list(c("lay", "n9")), annotations= "p < 0.001", y_position = 110, tip_length = 0.05, vjust = 0, color= "black" , textsize = 5 ) +
  geom_signif(comparisons=list(c("hatch", "n9")), annotations= "p < 0.001", y_position = 120, tip_length = 0.05, vjust = 0, color= "black" , textsize = 5 ) +
  geom_signif(comparisons=list(c("inc.d9", "hatch")), annotations= "p < 0.001", y_position = -5, tip_length = -0.05, vjust = 2, color= "black" , textsize = 5 ) +
  geom_signif(comparisons=list(c("inc.d9", "n9")), annotations= "p < 0.001", y_position = -15, tip_length = -0.05, vjust = 2, color= "black" , textsize = 5 )

#CORT
rechelleplot(cort.rechelle, "Corticosterone (ng/mL)")
